Numerous variables relating to 2016 election in 2021 US GSS^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis.git]

### 2022-03-19 outputs/paper/paper.Rmd
ggplot

# Data
```{r, include=FALSE, echo=FALSE}
reduced_data <- read_csv("outputs/data/prepared_gss.csv")
```
1.Conveying a sense of the dataset of interest.
2.Dicussion of the survey's methodology and its key features, strengths, weaknesses.
For instance what is the population, frame and sample.
How is the sample recruited 
what sampling approach is taken
what are some of the trade offs of this 
how is non response handled.
(What is good and bad about it

@@

```{r, echo=FALSE}
ggplot(reduced_data, aes(x = age)) +
  geom_bar(na.rm = T)

reduced_data %>%
  ggplot(aes(x = age, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate")

@@

reduced_data %>%
  ggplot(aes(x = pres16, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate")

reduced_data %>%
  ggplot(aes(x = gender, fill = gender)) +
  geom_bar() +
  scale_fill_brewer(palette = "pink")

reduced_data %>%
  ggplot(aes(x = race, fill = race)) +
  geom_bar() +
  scale_fill_brewer(palette = "green")

reduced_data %>%
  ggplot(aes(x = gender, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate")

reduced_data %>%
  ggplot(aes(x = degree, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate")

reduced_data %>%
  ggplot(aes(x = born_US, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate")

reduced_data$Family_income <- factor(reduced_data$Family_income, levels = c("Under $10,000","$10,000 ~ $19,999","$20,000 ~ $39,999","$40,000 ~ $59,999","$60,000 ~ $89,999","$90,000 ~ $129,999","$130,000 ~ $169,999","$170,000 or over"))
reduced_data %>%
  ggplot(aes(x = Family_income, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate") +
  coord_flip()

reduced_data %>%
  ggplot(aes(x = nation_education, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate")

reduced_data %>%
  ggplot(aes(x = nation_race, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate")

reduced_data %>%
  ggplot(aes(x = nation_arms, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate")

reduced_data %>%
  ggplot(aes(x = nation_welfare, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate")

reduced_data %>%
  ggplot(aes(x = Assistance_to_the_poor, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate")

reduced_data %>%
  ggplot(aes(x = Assistance_to_other_countries, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate")

reduced_data %>%
  ggplot(aes(x = social_security, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate")

reduced_data %>%
  ggplot(aes(x = race, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate")

@@

reduced_data %>%
  ggplot(aes(x = Immigration, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate") +
  coord_flip()

>>>>

# Data
```{r, include=FALSE, echo=FALSE}
reduced_data <- read_csv("outputs/data/prepared_gss.csv")
```
The data comes from US General Social Survey.
1.Conveying a sense of the dataset of interest.
2.Dicussion of the survey's methodology and its key features, strengths, weaknesses.
For instance what is the population, frame and sample.
How is the sample recruited 
what sampling approach is taken
what are some of the trade offs of this 
how is non response handled.
(What is good and bad about it

@@

```{r, echo=FALSE}
reduced_data %>%
  drop_na(age_group) %>%
  ggplot(aes(x = age_group, fill = age_group)) +
  geom_bar() +
  coord_flip() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Survey Respondents' Age",
       caption = "Figure 1: Distribution of survey respondents' age group") +
  theme(legend.position = "none")

reduced_data %>%
  ggplot(aes(x = race, fill = race)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Survey Respondents' race",
       caption = "Figure 2: Distribution of survey respondents' Race") +
  theme(legend.position = "none")

# reduced_data %>%
#   ggplot(aes(x = age, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
#   geom_bar() +
#   scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
#   labs(fil = "Candidate")

@@

reduced_data %>%
  drop_na(nation_race) %>%
  ggplot(aes(x = race, fill = nation_race)) +
  geom_bar() +
  coord_flip() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Opinion on National Spending on Improving Conditions of Black Population",
       caption = "Figure 3: Distribution of survey respondents' Race") +
  facet_wrap(~ pres16)

reduced_data %>%
  ggplot(aes(x = pres16, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate")

# reduced_data %>%
#   ggplot(aes(x = gender, fill = gender)) +
#   geom_bar() +
#   scale_fill_brewer(palette = "pink")

reduced_data %>%
  ggplot(aes(x = gender, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate")

reduced_data %>%
  ggplot(aes(x = degree, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate")

reduced_data %>%
  ggplot(aes(x = born_US, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate")

reduced_data$Family_income <- factor(reduced_data$Family_income, 
                                     levels = c("Under $10,000","$10,000 ~ $19,999","$20,000 ~ $39,999","$40,000 ~ $59,999", 
                                                "$60,000 ~ $89,999","$90,000 ~ $129,999","$130,000 ~ $169,999","$170,000 or over"))
reduced_data %>%
  ggplot(aes(x = Family_income, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate") +
  coord_flip()

reduced_data %>%
  ggplot(aes(x = nation_education, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate")

reduced_data %>%
  ggplot(aes(x = nation_race, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate")

reduced_data %>%
  ggplot(aes(x = nation_arms, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate")

reduced_data %>%
  ggplot(aes(x = nation_welfare, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate")

reduced_data %>%
  ggplot(aes(x = Assistance_to_the_poor, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate")

reduced_data %>%
  ggplot(aes(x = Assistance_to_other_countries, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate")

reduced_data %>%
  ggplot(aes(x = social_security, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate")

reduced_data %>%
  ggplot(aes(x = race, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate")

@@

reduced_data %>%
  ggplot(aes(x = Immigration, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate") +
  coord_flip()
